Gaussian mean estimation in simulated data sets

### 2019-12-20 analysis/gaussmeanest.Rmd
wflow_publish("gaussmeanest.Rmd")

```{r load-pkgs, message=FALSE, warning=FALSE}
library(ggplot2)
library(cowplot)
source("../code/signals.R")
```

@@

```{r load-results}
load("../output/dscr.RData")
```

@@

This plot shows the mean function as a block line, and the +/- 2
standard deviations as orange lines:

```{r spikes-signal, fig.height=4, fig.width=6}
t         <- (1:1024)/1024
mu        <- spikes.fn(t,"mean")
sigma.ini <- sqrt(cblocks.fn(t,"var"))
sd.fn     <- sigma.ini/mean(sigma.ini) * sd(mu)/3
par(cex.axis = 1,cex.lab = 1.25)
plot(mu,type = "l", ylim = c(-0.05,1),xlab = "position",ylab = "",
     lwd = 1.75,xaxp = c(0,1024,4),yaxp = c(0,1,4))
lines(mu + 2*sd.fn,col = "darkorange",lty = 5,lwd = 1.75)
lines(mu - 2*sd.fn,col = "darkorange",lty = 5,lwd = 1.75)
```

@@

This plot shows the mean function as a block line, and the +/- 2
standard deviations as orange lines:

@@

>>>>

```{r load-pkgs, message=FALSE, warning=FALSE}
library(smashr)
library(ggplot2)
library(cowplot)
source("../code/signals.R")
```

@@

```{r load-results, warning=FALSE}
load("../output/dscr.RData")
```

@@

This plot shows the mean function as a black line, and the +/- 2
standard deviations as orange lines:

```{r spikes-signal, fig.height=4, fig.width=6}
t         <- (1:1024)/1024
mu        <- spike.fn(t,"mean")
sigma.ini <- sqrt(cblocks.fn(t,"var"))
sd.fn     <- sigma.ini/mean(sigma.ini) * sd(mu)/3
par(cex.axis = 1,cex.lab = 1.25)
plot(mu,type = "l", ylim = c(-0.05,1),xlab = "position",ylab = "",
     lwd = 1.75,xaxp = c(0,1024,4),yaxp = c(0,1,4))
lines(mu + 2*sd.fn,col = "darkorange",lty = 5,lwd = 1.75)
lines(mu - 2*sd.fn,col = "darkorange",lty = 5,lwd = 1.75)
```
Now, we plot the ground-truth signal (the mean function, drawn as
a black line) and the signals recovered by TI thresholding (light blue
line) and SMASH (the red line) for one simulated dataset as an illustration

```{r spikes-signal-with-estimates, fig.height=4, fig.width=6}
t         <- (1:1024)/1024
mu        <- spike.fn(t,"mean")
sigma.ini <- sqrt(cblocks.fn(t,"var"))
sd.fn     <- sigma.ini/mean(sigma.ini) * sd(mu)/3
x.sim  <- rnorm(1024,mu,sd.fn)
mu.smash <- smash(x.sim,family = "DaubLeAsymm",filter.number = 8)
mu.ti    <- ti.thresh(x.sim,method = "rmad",family = "DaubLeAsymm",
                      filter.number = 8)
par(cex.axis = 1)
plot(mu,type = "l",col = "black",lwd = 3,xlab = "position",ylab = "",
     ylim = c(-0.05,1),xaxp = c(0,1024,4),yaxp = c(0,1,4))
lines(mu.ti,col = "dodgerblue",lwd = 3)
lines(mu.smash,col = "orangered",lwd = 3)
```

@@

This plot shows the mean function as a black line, and the +/- 2
standard deviations as orange lines:

@@

Now, we plot the ground-truth signal (the mean function, drawn as
a black line) and the signals recovered by TI thresholding (light blue
line) and SMASH (the red line) for one simulated dataset as an illustration

```{r corner-signal-with-estimates, fig.height=4, fig.width=6}
t         <- (1:1024)/1024
mu        <- cor.fn(t,"mean") 
sigma.ini <- sqrt(doppler.fn(t,"var"))
sd.fn     <- sigma.ini/mean(sigma.ini) * sd(mu)/3
x.sim  <- rnorm(1024,mu,sd.fn)
mu.smash <- smash(x.sim,family = "DaubLeAsymm",filter.number = 8)
mu.ti    <- ti.thresh(x.sim,method = "rmad",family = "DaubLeAsymm",
                      filter.number = 8)
par(cex.axis = 1)
plot(mu,type = "l",col = "black",lwd = 3,xlab = "position",ylab = "",
     ylim = c(-0.05,1),xaxp = c(0,1024,4),yaxp = c(0,1,4))
lines(mu.ti,col = "dodgerblue",lwd = 3)
lines(mu.smash,col = "orangered",lwd = 3)
```
